---
title: "Exercise_economist"
author: Anna Bonnevie
date: 2026-01-22
format: html
editor: visual
theme: cosmo
code-fold: true
---

# Exercise on economist scatterplot in Quarto

## This exercise is part of the doctoral course "Data handling and high quality illustrations for publications" at SLU.

### Script from previous exercise has been used in the present one, to practice using Quarto, Github and to provide understandable script for reproducibility.

Download the library readr. The data file used is data_economist.csv, found [here](https://www.dropbox.com/s/7imn0eoey9ckxh5/data_economist.csv?dl=1). Make a new data frame named "ec".

```{r}
#| echo: false
#| message: false
#| warning: false
#| include: false
library(readr) 
library(ggplot2)
ec <- read_csv("https://www.dropbox.com/s/7imn0eoey9ckxh5/data_economist.csv?dl=1") 
```

Visualise the first rows of ec, and the structure of the file.

```{r}
head(ec)
str(ec)
```

Now, have a look at the Regions in ec.

```{R}
#| message: false
#| warning: false
levels(ec$Region)
```

Rename the regions to the following: "OECD", "Americas", "Asia & Oceania", "Central & Eastern Europe", "Middle East & north Africa", "Sub-Saharan Africa". Add radbrytning before "Oceania", "Easern", "north" and the last "Africa".

```{R}
#| message: false
#| warning: false
#| include: false
ec$Region <- factor(ec$Region, levels = c("EU W. Europe", "Americas", "Asia Pacifics", "East EU Cemt Asia", "MENA", "SSA"), labels = c("OECD", "Americas", "Asia & \nOceania", "Central & \nEastern Europe", "Middle East & \nnorth Africa", "Sub-Saharan \nAfrica"))

levels(ec$Region)
```

```{r}
ggplot(data = ec, aes(x=CPI, y= HDI, colour = Region)) + geom_point(shape=21, size=3, stroke=0.8, fill="white") + geom_smooth(method = "lm", formula = y~poly(x,2), se=F, size=0.6, color = "red")

```
